Predictive modeling using genomic annotations

### 2018-10-03 Manuscript/manuscript.Rmd
updates

It was found that the multiple logistic regression models utilizing random over and under-sampling out-performed the other techniques and were comparatively similar with F1 scores of 0.636 and 0.637 respectively. The under-technique was evaluated over 13 iterations, while the over-sampling technique took far more iterations for the cumulative mean F1 score to converge, X to be exact. Given that and the fact that the under-sampling technique uses significantly less data than the over-sampling, while still performing at the same level, it was concluded that this was the best balancing technique and used in further analyses.

@@

##

>>>>

It was found that the multiple logistic regression models utilizing random over and under-sampling out-performed the other techniques and were comparatively similar with F1 scores of 0.636 and 0.637 respectively. The under- sampling technique was evaluated over 13 iterations, while the over-sampling technique took far more iterations for the cumulative mean F1 score to converge, 26 to be exact. Given that and the fact that the under-sampling technique uses significantly less data than the over-sampling, while still performing at the same level, it was concluded that this was the best balancing technique and used in further analyses.

@@

## X Classification Algorithm Provides Best Performance
